%        File: notes.tex
%     Created: Fri Jan 04 08:00 AM 2013 I
% Last Change: Fri Jan 04 08:00 AM 2013 I
%
\documentclass[a4paper]{article}
\usepackage{listings}
\usepackage[pdftex]{graphicx}
\usepackage{float}
\usepackage{graphics}
\usepackage[T1]{fontenc}
\usepackage[scaled]{helvet}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[cm]{fullpage}

\begin{document}
\large

\title{Notes and Learnings}
\date{\today}
\maketitle

\tableofcontents
\listoffigures
\pagebreak

\section{General / Random Thoughts}
\begin{itemize}
  \item I can currently think of 4 avenues of generating income :
    \begin{enumerate}
      \item Employment - currently 100\%, but by 2020, my goal is to reduce this contribution go 50\%
      \item Rental - currently 0, possiblity of achiving 7 - 12 L / annum using current assets and funds ( 2 - 3 yr effort )
      \item Investing in Stocks - no clue, but a viable strategy if some time is put into it. Also if some learning is put into it, I can use it for the lenght of my lifetime to generate assets sitting at home.
      \item Self Employment / Business - Few possiblities are Shrig's beauty saloon
    \end{enumerate}
  \item Given the above, I have no good traction on the 2020 goal
  \item Always have liquid reserves to survive upto 3 years without any support - currently met ( 8 L per annum )
\end{itemize}

\section{Notes from Jan3/4}
\begin{itemize}
  \item Do not spend useless 'mind' time on worry slots, instead be resourceful and spend those cycles on actual problems
  \item THere is no room for 'worry' and 'excited' time when you sit down to research stocks. Time cannot be expanded by worrying. And decisions are going to be bad and not objective. So leave the 'worry' outside the door and ask it to wait till you are done.
  \item CRISIL IER reports a must and any other independent research. This saved some speculation on Asianana Housing. These show thier independent alaysis of what the fair price of the stock is which will give an indicator of 'when' to enter if it is a fundamentally good business.
  \item Watch list 1
  \item Look for high 'dividiend yield' plays
  \item Look for MFs which are run purely by the Buffet principle.
  \item Learn how to value and estimate future price of the company as this is the the only true measure a stock should be owned.
  \item Use the PEG ratio as an indicator
  \item Keep notes and logs of learnings and findings
\end{itemize}

\section{Notes from Jan5-6}
\begin{itemize}
  \item American company value plays : AAPL, IBM
  \item Possible good growht - Baidu, Cognizant
  \item Possible small cap - high growwht Ebix, Klic, GMCR, See ( http://seekingalpha.com/article/1088781-6-high-growth-stocks-in-an-uptrend-with-very-low-peg-ratios )
  \item Need action on AAPL, IBM
  \item Zynga seems to be cheap.
\end{itemize}

\section{Notes from Jan7}
\subsection{Long term thoughts}
\begin{itemize}
  \item We know that the industrial world is at the limits of scalign as the world works today. If you simply play the game with the axiom / model of the current economic theory, then in the long term 20-30 yrs I think you are going to lose out. Thinkt about if this whole system crumbles and falls into itself what will survive, what are the new things that will come up?
  \item The world has become fat and exploding - population is out of control, resources are being consumed at a faster rate, resournces which provide luxury and non-essentails is actually driving the economy. A lot of things are going to collaspe
  \item Eg. Amazon's model is all about increasing efficieny in the process - retail and computing resources. Also the move from books to ebooks moarket is all about making the original process/concept revolutionarily by keeping the original value of the concept the same. If this was not done, books would have become extinct in 10 years. Can you think of anything else which follows this model, other companies which think something like this.
  \item Make a list of all non-essential things which will collapse and will not be necessary at all
  \item Make a list of essential things which are required and will collapse - how will it be replaced, how are reduced resources going to increase the prices
  \item If monetary system collapses, what will be of value. Eg. Gold is inessential to daily life, yet it commands pseudo-value today. At the brink of collapse, Gold will not have anyw value. Food and Water will have value. Alternatives to natural food and water are going to have value. Who is manufacturing synthesized water? What is cost? Water from sea.
  \item Play scenarios of full collapse and partial collapse. Play scenarios of more realistic collapse w.r.t population demographic models etc.
\end{itemize}
\begin{itemize}
  \item Use Google Trends to check long term trends
  \item See how you can use BigML for some modellling ( http://seekingalpha.com/article/1096551-dividends-still-the-best-all-season-investment-strategy )
  \item Allocation ideas : Dividend Play, Value Play - Blue chip long term, Small Cap Growth, Index Funds, reits
\end{itemize}

\end{document}


